Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
still fixing up explanation/details of MCMC procedure

We then estimate the parameters and their covariances by performing 10000 steps
during which we keep track of the proposed $T_{2, j}$ and $\tilde{I}_{545, j}$ 
values at the $j^{th}$ step since the end of burn-in. From these 2000 samples, 
we compute estimates of each parameter, $T_2$ = $\langle T_{2, j} \rangle$, 
$\tilde{I}_{545}$ = $\langle \tilde{I}_{545, j} \rangle$, and of each 
parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
$\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the 
corresponding estimate of the monochromatic two-component intensity at 545 GHz,
$M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
$M_{545}$ is of more general utility in making foreground predictions because 
it provides the normalization for the two-component spectrum $M_{\nu}$, 
independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
function $S_{545}$ calculated according to Equation \ref{eqn:source}.

>>>>

We then estimate the parameters and their uncertainties by performing 10,000 
sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the proposed 
parameter values at the $j^{th}$ step since the end of burn-in. From these 
10,000 samples, we compute estimates of each parameter's mean, 
$\langle T_2 \rangle$ = $\langle T_{2, j} \rangle$, 
$\langle \tilde{I}_{545} \rangle$ = $\langle \tilde{I}_{545, j} \rangle$, of 
each parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$, 
$\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$ and of the covariance 
$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=$\langle T_{2,j}-\langle T_2 \rangle 
\rangle \langle \tilde{I}_{545, j} - \langle \tilde{I}_{545} \rangle \rangle$.

We also compute the corresponding estimate of the monochromatic two-component 
intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
$M_{545}$ is of more general utility in making foreground predictions because 
it provides the normalization for the two-component spectrum $M_{\nu}$, 
independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
function $S_{545}$ calculated according to Equation \ref{eqn:source}.
